---
title: Export
author: Rebecca Hoffmann
date: '2021-01-09'
slug: export
categories: []
tags: []
draft: false
output:
  blogdown::html_page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```
### Las libraría utilizadas:

```{r libraries, warning=FALSE, message=F}
library(tidyverse)
library(tradestatistics)
library(ggplot2)
library(rworldmap)
library(treemapify)
library(ggthemes)
library(scales)
```

## Los datos
Descargo el base de datos:
I rename the column "reporter_iso" to be able to merge it with the second data frame from Open Trade Statistics:
```{r comercio API 1, message=FALSE}
comercio_mundo_api <- tradestatistics::ots_create_tidy_data(
  years = 2018, 
  reporters = "all", 
  partners = "all", 
  products = "all") %>%
  rename(country_iso = 'reporter_iso')
```

From another data base in Open Trade Statistics, I can choose only countries belonging to the continent of The Americas:

```{r comercio API 2, message=FALSE}
countries_LATAM <- tradestatistics::ots_countries %>%
  filter(continent == "Americas") 
```

Merging the two data frames, I now get a data frame including information only for the region of the Americas.

```{r comercio LATAM merge, message=FALSE}
comercio_latam <- merge(x = comercio_mundo_api, y = countries_LATAM,
      by = "country_iso")
```

## Transformando los datos
I select the row that I want to use to create the map with, however, I leave the data frame with all the info for trade in Latin America, so I can return and use it for another graph.

```{r comercio LATAM select, message=FALSE}
comercio_latam_import <- comercio_latam %>%
  select(country_iso,
         reporter_fullname_english,
         import_value_usd) %>%
  drop_na()
```
