---
title: Export
author: Rebecca Hoffmann
date: '2021-01-09'
slug: export
categories: []
tags: []
draft: false
output:
  blogdown::html_page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```
### Las libraría utilizadas:

```{r libraries, warning=FALSE, message=F}
library(tidyverse)
library(tradestatistics)
library(ggplot2)
library(ggthemes)
library(scales)
library(patchwork)
```

## Los datos
Descargo el base de datos:
I rename the column "reporter_iso" to be able to merge it with the second data frame from Open Trade Statistics:
```{r comercio API 1, message=FALSE}
comercio_mundo_api <- tradestatistics::ots_create_tidy_data(
  years = 2018, 
  reporters = "all", 
  partners = "all", 
  products = "all") %>%
  rename(country_iso = 'reporter_iso')
```

From another data base in Open Trade Statistics, I can choose only countries belonging to the continent of The Americas:

```{r comercio API 2, message=FALSE}
countries_LATAM <- tradestatistics::ots_countries %>%
  filter(continent == "Americas") 
```

Merging the two data frames, I now get a data frame including information only for the region of the Americas.

```{r comercio LATAM merge, message=FALSE}
comercio_latam <- merge(x = comercio_mundo_api, y = countries_LATAM,
      by = "country_iso") %>%
  select(country_iso,
         reporter_fullname_english,
         export_value_usd,
         top_export_product_code)
```

## Transformando los datos
I select the row that I want to use to create the map with, however, I leave the data frame with all the info for trade in Latin America, so I can return and use it for another graph.

```{r comercio LATAM productos, message=FALSE}
productos_latam <- tradestatistics::ots_products_shortnames %>%
  rename(top_export_product_code = "product_code")

productos_latam_export <- merge(x = comercio_latam, 
                                y = productos_latam, 
                                by = 'top_export_product_code') %>%
    filter(
         reporter_fullname_english != "USA, Puerto Rico and US Virgin Islands (excludes Virgin Islands until 1981)",
         reporter_fullname_english != "Canada",
         reporter_fullname_english != "Greenland",
         reporter_fullname_english != "Br. Virgin Isds",
         reporter_fullname_english != "United States Minor Outlying Islands",
         reporter_fullname_english != "South Georgia and the South Sandwich Islands")
```

```{r LATAM factor, message=FALSE}
export_countries_modificado <- productos_latam_export %>%
  mutate(reporter_fullname_english = as.factor(reporter_fullname_english)) %>%
mutate(reporter_fullname_english = fct_collapse(reporter_fullname_english,
            "Caribbean" = c("Anguilla",
                            "Neth. Antilles",
                            "Antigua and Barbuda",
                            "Bahamas",
                            "Barbados",
                            "Belize",
                            "Bermuda",
                            "Bouvet Island",
                            "Cocos Isds",
                            "Cayman Isds",
                            "Cuba",
                            "Grenada",
                            "Guyana",
                            "Haiti",
                            "Jamaica",
                            "Saint Kitts and Nevis (includes Anguilla until 1981)",
                            "Saint Lucia",
                            "Montserrat",
                            "Saint Pierre and Miquelon",
                            "Suriname",
                            "Turks and Caicos Isds",
                            "Trinidad and Tobago",
                            "Saint Vincent and the Grenadines"),
      "Central America" = c("Costa Rica",
                            "Dominica",
                            "Dominican Rep.",
                            "El Salvador",
                            "Guatemala",
                            "Honduras",
                            "Nicaragua",
                            "Panama (excludes Panama Canal Zone until 1978)"),
             "Argentina" = c("Argentina", 
                             "Falkland Isds (Malvinas)")))
```

```{r LATAM productos modificar, message=FALSE}
export_countries_2018 <- export_countries_modificado %>%
  group_by(reporter_fullname_english, 
           product_shortname_english,
           export_value_usd) %>%
  summarise(export_value_usd = sum(export_value_usd, na.rm = T)) %>%
  arrange(desc(export_value_usd)) %>%
  drop_na()
```

### Graficando
```{r comercio LATAM productos graficar, message=FALSE}
latam_graph <- ggplot(export_countries_2018, aes(
  x = reporter_fullname_english,
  y = export_value_usd,
  fill = product_shortname_english)) +
    geom_col() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    title = "Exportaciones por producto (2018)",
    caption = "Fuerte: Open Trade Statistics") +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_economist() +
  theme(legend.position = "bottom") +
  coord_flip()

latam_graph
```

```{r comercio LATAM w/o Caribbean, message=FALSE}
latam_reduced <- export_countries_modificado %>%
  filter(reporter_fullname_english != "Caribbean",
         reporter_fullname_english != "Central America")
  
latam_graph1 <- ggplot(latam_reduced, aes(
  x = reporter_fullname_english,
  y = export_value_usd,
  fill = product_shortname_english)) +
    geom_col() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    title = "Exportaciones por producto (2018)",
    caption = "Fuerte: Open Trade Statistics") +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_economist() +
  theme(legend.position = "bottom") +
  coord_flip()

latam_graph1
```
```{r comercio Caribbean, message=FALSE}
comercio_caribbean <- productos_latam_export %>%
  filter(reporter_fullname_english != "Argentina",
         reporter_fullname_english != "Bolivia",
         reporter_fullname_english != "Brasil",
         reporter_fullname_english != "Chile",
         reporter_fullname_english != "Colombia",
         reporter_fullname_english != "Ecuador",
         reporter_fullname_english != "Mexico",
         reporter_fullname_english != "Paraguay",
         reporter_fullname_english != "Peru",
         reporter_fullname_english != "Uruguay",
         reporter_fullname_english != "Venezuela") %>%
  group_by(reporter_fullname_english, 
           product_shortname_english,
           export_value_usd) %>%
  summarise(export_value_usd = sum(export_value_usd, na.rm = T))

caribbean_graph <- ggplot(comercio_caribbean, aes(
  x = reporter_fullname_english,
  y = export_value_usd,
  fill = product_shortname_english)) +
    geom_col() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    title = "Exportaciones por producto el Caribe (2018)",
    caption = "Fuerte: Open Trade Statistics") +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_economist() +
  theme(legend.position = "bottom") +
  coord_flip()

caribbean_graph
```

```{r comercio patchwork, message=FALSE}
(latam_graph | latam_graph1 | caribbean_graph)
```