---
title: Datos Historicos del Comercio Exterior de América Latina
author: Rebecca Hoffmann
date: '2020-12-07'
slug: datos-historicos
categories: []
tags: []
draft: false
output:
  blogdown::html_page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

En este post, querría analizar la evolución del comercio en la región de América Latin utilizando el base de dato de Open Trade Statistics:

### Las libraría utilizadas:

```{r libraries, message=F}
library(tidyverse)
library(tradestatistics)
library(ggplot2)
```
## Los datos
Descargo el base de datos:
I rename the column "reporter_iso" to be able to merge it with the second data frame from Open Trade Statistics:
```{r comercio API 1, message=FALSE}
comercio_mundo_api <- tradestatistics::ots_create_tidy_data(
  years = 1980:2018, 
  reporters = "all", 
  partners = "all") %>%
  rename(country_iso = 'reporter_iso')
```

From another data base in Open Trade Statistics, I can choose only countries belonging to the continent of The Americas:

```{r comercio API 2, message=FALSE}
countries_LATAM <- tradestatistics::ots_countries %>%
  filter(continent == "Americas") 
```

Merging the two data frames, I now get a data frame including information only for the region of the Americas.

However, I only want to include information about Latin American countries. So, I also exclude the US, Canada, Greenland, and some minor US island from the analysis:

```{r comercio LATAM merge, message=FALSE}
comercio_latam_reducido <- merge(x = comercio_mundo_api, y = countries_LATAM,
      by = "country_iso") %>%
  select(year,
         country_iso,
         country_fullname_english, 
         export_value_usd) %>%
  filter(country_iso != "usa", # Excluding the U.S.
         country_iso != "can", # Excluding Canada
         country_iso != "grl", # Excluding Greenland
         country_iso != "vir", # Excluding one observation of US Virgin Islands
         country_iso != "umi", # Excluding "United States Minor Outlying Islands"
         country_iso != "vgb", # Excluding British Virgin Islands
         country_iso != "sgs") # Exclude South Georgia and the South Sandwich Islands (British territory)


comercio_latam_reducido

```

## Transformando los datos
Before, I graph the results, I want to merge all the Caribbean countries into one category for the Caribbean countries:

```{r comercio Americas, message=FALSE}

comercio_latam_modificado <- comercio_latam_reducido %>%
  mutate(country_fullname_english = as.factor(country_fullname_english))

comercio_latam_caribbean <- comercio_latam_modificado %>%
  select(year,
         country_fullname_english,
         export_value_usd) %>%
  mutate(country_fullname_english = fct_collapse(country_fullname_english,
                                  "Caribbean" = c("Anguilla", 
                                                  "Neth. Antilles", 
                                                  "Antigua and Barbuda", 
                                                  "Bahamas",
                                                  "Barbados",
                                                  "Belize",
                                                  "Bermuda",
                                                  "Bouvet Island",
                                                  "Cocos Isds",
                                                  "Cayman Isds",
                                                  "Guadeloupe",
                                                  "Cuba",
                                                  "Grenada",
                                                  "French Guiana",
                                                  "Guyana",
                                                  "Haiti",
                                                  "Jamaica",
                                                  "Saint Kitts and Nevis (includes Anguilla until 1981)",
                                                  "Saint Lucia",
                                                  "Montserrat",
                                                  "Martinique",
                                                  "Saint Pierre and Miquelon",
                                                  "Suriname",
                                                  "Turks and Caicos Isds",
                                                  "Trinidad and Tobago",
                                                  "Saint Vincent and the Grenadines"),
                                  "Central America" = c("Costa Rica",
                                                        "Dominica",
                                                        "Dominican Rep.",
                                                        "El Salvador",
                                                        "Guatemala",
                                                        "Honduras",
                                                        "Nicaragua",
                                                        "Panama (excludes Panama Canal Zone until 1978)"),
                                  "Argentina" = c("Argentina", "Falkland Isds (Malvinas)")))

```

## Graficando
```{r comercio LATAM graph, message=FALSE}
ggplot(comercio_latam_caribbean) +
  geom_line(aes(year,
                export_value_usd,
                group = country_fullname_english,
                color = country_fullname_english)) +
  labs(title = "Evolución de exportación en América Latina",
       y = "export en USD",
       x = "Año") +
  theme(legend.position = "bottom")
```

trying to make a bar chat as well:
